Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-23 cav2017/cav2017.tex
added experimental objectives

%-------------------------------
\subsection{Description of the benchmarks}
%-------------------------------

A set of state-space models for different classes of 
systems were extracted from the literature and employed 
for validating our automated synthesis methodology. 
All the systems are SISO models of the following form:
%
\begin{equation}
\left\lbrace\begin{array}{c}
\dot{\textbf{x}}(t)=\textbf{A}\textbf{x}(t)+\textbf{B}u(t)\\
y(t)=\textbf{C}\textbf{x}(t)+\textbf{D}u(t)
\end{array}\right.
\end{equation}

Table~\ref{table:State-space benchmarks} summarises all benchmarks extracted 
from the control system literature~\cite{Franklin15,maglev,converters,CTMS}. 
\textit{DC Motor Position and Rate} plants describes the angular position and 
velocity of a DC Motor, respectively, that coupled with wheels and cables provides 
translational motion. 
\textit{Aircraft Pitch Dynamics} plant represents the air vehicle orientation and 
control based on the pitch dimension. 
\textit{Ball Magnetic Levitation} plant describes a physical model to keep a 
metal ball hanged in air via a magnetic field . 
\textit{Buck Converter} plant represents a power converter model that steps down 
voltage from the supply to the load while stepping up current. 
\textit{Boost Converter} plant also represents a power converter model, but here 
it steps up voltage from the supply to the load while stepping down current. 
\textit{Buck-boost Converter} plant represents a converter model that has an output 
voltage magnitude, which is either greater than or less than the input voltage magnitude.

@@

We have also conducted the experimental evaluation on a 12-core 2.40 GHz
Intel Xeon E5-2440 with 96 GB of RAM and Linux OS. All times given are wall 
clock time in seconds as measured by the UNIX date command.

@@

>>>>

%-------------------------------
\subsection{Description of the benchmarks}
\label{experimental-setup}
%-------------------------------

A set of state-space models for different classes of 
systems were extracted from the 
literature~\cite{Franklin15,maglev,converters,CTMS} 
and employed for validating our methodology. 
%All systems are SISO models of the following form:
%
%\begin{equation}
%\left\lbrace\begin{array}{c}
%\dot{\textbf{x}}(t)=\textbf{A}\textbf{x}(t)+\textbf{B}u(t)\\
%y(t)=\textbf{C}\textbf{x}(t)+\textbf{D}u(t)
%\end{array}\right.
%\end{equation}
%
Table~\ref{table:State-space benchmarks} summarizes 
all our benchmarks, which are SISO models (cf. section~\ref{sec:preliminaries}).

\textit{DC Motor Position and Rate} plants describes the angular position and 
velocity of a DC Motor, respectively. 
\textit{Aircraft Pitch Dynamics} plant represents the air vehicle orientation and 
control based on the pitch dimension. 
\textit{Ball Magnetic Levitation} plant describes a physical model to keep a 
metal ball hanged in air via a magnetic field . 
\textit{Buck Converter} plant represents a power converter model that steps down 
voltage from the supply to the load while stepping up current. 
\textit{Boost Converter} plant also represents a power converter model, but here 
it steps up voltage from the supply to the load while stepping down current. 
\textit{Buck-boost Converter} plant represents a converter model that has an output 
voltage magnitude, which is either greater than or less than the input voltage magnitude.

@@

We have conducted the experimental evaluation on a 12-core 2.40 GHz
Intel Xeon E5-2440 with 96 GB of RAM and Linux OS. All times given are wall 
clock time in seconds as measured by the UNIX date command.

@@

Using the state-space models given in Section~\ref{experimental-setup}, 
our experimental evaluation aims to answer two research questions:
%
\begin{enumerate}

\item[RQ1] \textbf{(CEGIS)} do the CEGIS with multi-stage 
verification and abstraction refinement generate a FWL digital 
controller in a reasonable amount of time?

\item[RQ2] \textbf{(sanity check)} are the synthesized controllers sound
and can their stability and safety be confirmed outside of our model?

\end{enumerate}
